Analysis paper

### 2021-08-11 analysis/analysis.Rmd
update plots

  # median performance
  p_median <- 
    plot_helper(scores, y = "interval_score_0.5") + 
    labs(y = "median WIS", x = NULL)

@@

  p_cov90 <- scores[range %in% c(90)] %>%
    plot_helper(y = "coverage", rel = FALSE) + 
    geom_hline(yintercept = 0.5, linetype = "dashed") +
    labs(y = "Coverage - 50% PI", x = xlabel) + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)

  p_combined <- (p_mean + p_median) / 
    (p_aem + p_wis_sd) / 
    (p_sharpness + p_bias) / 
    (p_cov50 + p_cov90) +  
    plot_layout(guides = "collect") & 
    plot_annotation(tag_levels = 'A') &
    theme(legend.position = 'bottom')

>>>>

@@

  p_cov90 <- scores[range %in% c(90)] %>%
    plot_helper(y = "coverage", rel = FALSE) + 
    geom_hline(yintercept = 0.9, linetype = "dashed") +
    labs(y = "Coverage - 90% PI", x = xlabel) + 
    expand_limits(y=c(0, 1)) + 
    scale_y_continuous(labels = scales::percent)

  p_combined <- (p_mean + p_aem) / 
    (p_sharpness + p_bias) / 
    (p_cov50 + p_cov90) /
    (p_wis_sd) +  
    plot_layout(guides = "collect") & 
    plot_annotation(tag_levels = 'A') &
    theme(legend.position = 'bottom')
